On Sample Size for Block Bootstrap Confidence Intervals to Have Desired Coverage Rates

### 2023-05-16 Manuscript/manuscript.tex
abstract rewritten

\author{Mathew Chandy
%   \href{mailto:mathew.chandy@uconn.edu}
% {\nolinkurl{mathew.chandy@uconn.edu}}\\
  and Jun Yan\\[1ex]
  Department of Statistics, University of Connecticut\\
}
\date{}

@@

\begin{abstract}
Block bootstrap is a method that is useful for estimating a parameter of a time
series. Theoretically, the method will work perfectly given an infinitely
large sample of the time series. It is necessary to know how large of a finite
sample is required for block bootstrap estimation to work. Before this study,
there have been no investigations into this problem within the literature. The
aim of this study is to answer this question by simulating replications of
block bootstrap interval estimations of a parameter of a time series, and
recording the rate at which the parameter is recovered by each replicate
interval. The sample length required for acceptable performance is
unsurprisingly found to be dependent on the type of interval construction and
the series' level of temporal dependence.

@@

\jy{Practice my writing tips on latex (e.g., keep line width under 80; use
  double blank lines to separate paragraphs; etc.):
  \url{
https://statds.github.io/stat-writing/using-the-right-tools-for-writing.html},
  chapter 2}

@@

The necessary sample size for bootstrap standard errors to provide valid
uncertainty measures in practice has not been extensively studied. For
independent data and non-block bootstrap, \citet{hesterberg2015teachers} notes
that while percentile-based CIs from nonparametric bootstrap
are more accurate than $t$-intervals for larger sample sizes, they are
less accurate for smaller sample sizes. In the context of structural equation
modeling, \citet{nevitt2001performance} find
that a sample size of 200--1000 is usually sufficient for interval estimation
using standard nonparametric bootstrap. For dependent data, the necessary
sample
size for block bootstrap is even less clear. In a linear regression setting
with
dependent data, \citet{goncalves2005bootstrap} find that standard error
estimates from block bootstrap in small samples may be more accurate than
inference from closed-form asymptotic estimates, but block bootstrap percentile
CIs still do not have sufficient coverage even for sample size
$n = 1024$.

>>>>

\author{Mathew Chandy, Elizabeth Schifano,
%   \href{mailto:mathew.chandy@uconn.edu}
% {\nolinkurl{mathew.chandy@uconn.edu}}\\
  and Jun Yan\\[1ex]
  Department of Statistics, University of Connecticut\\
}
\date{}

@@

\begin{abstract}
Block bootstrap is widely used in constructing confidence intervals for
parameters estimated from stationary time series. Theoretically, the method
should provide valid confidence intervals as the length of the time series goes
to infinity. In practice, however, it is necessary to know how large of a finite
sample is required for block bootstrap confidence intervals to work well. This
study aims to answer this question in a simple simulation setting where the data
are generated from an autoregressive process of order~1. The empirical coverage
rates of several commonly used bootstrap confidence intervals for the mean,
standard deviation, and the lag-1 autocorrelation are compared. \jy{put most
  notable findings here. Possibly 1) large sample is needed; percentile
  bootstrap is not working well for rho (can we offer some explanation?).}

@@

@@

The necessary sample size for bootstrap standard errors to provide valid
uncertainty measures in practice has not been extensively studied. For
independent data and non-block bootstrap, \citet{hesterberg2015teachers} notes
that while percentile-based CIs from nonparametric bootstrap
are more accurate than $t$-intervals for larger sample sizes, they are
less accurate for smaller sample sizes. In the context of structural equation
modeling, \citet{nevitt2001performance} find
that a sample size of 200--1000 is usually sufficient for interval estimation
using standard nonparametric bootstrap. For dependent data, the necessary
sample
size for block bootstrap is even less clear. In a linear regression setting
with
dependent data, \citet{goncalves2005bootstrap} find that standard error
estimates from block bootstrap in small samples may be more accurate than
inference from closed-form asymptotic estimates, but block bootstrap percentile
\jy{did they do block or standard bootstrap?}
CIs still do not have sufficient coverage even for sample size
$n = 1024$.
